### 2021-04-27 preliminaries.tex
Reword two paragraphs
following suggestions from Grammarly.

Since the space of derivable clauses is typically very large,
the efficacy of the prover depends on the order in which the inferences are applied.
The standard saturation-based \glspl{atp} order the inferences
by maintaining two classes of inferred clauses: processed and unprocessed \cite{Schulz2019}.
In each \emph{iteration of the saturation loop}, one clause (so-called \emph{given clause})
is selected from the unprocessed set
and all the inferences between the given clause and the processed clauses are performed.
The resulting new clauses are added to the unprocessed set.
Finishing the proof in few iterations of the saturation loop is important
because the number of inferred clauses typically grows exponentially during the proof search.

@@

The \emph{superposition calculus} is of particular interest
because it is used in the most successful contemporary \gls{fol} \glspl{atp}.
The inferences of the superposition calculus are constrained by a \emph{\gls{sot}} \cite{DBLP:journals/logcom/BachmairG94}.

>>>>

Since the space of derivable clauses is typically very large,
the efficacy of the prover depends on the order in which the inferences are applied.
The standard saturation-based \glspl{atp} order the inferences
by maintaining two classes of inferred clauses: processed and unprocessed \cite{Schulz2019}.
In each \emph{iteration of the saturation loop}, one clause (so-called \emph{given clause})
is combined with all the processed clauses for inferences.
The resulting new clauses and the given clause are added to the unprocessed set and the processed set, respectively.
Finishing the proof in few iterations of the saturation loop is important
because the number of inferred clauses typically grows exponentially during the proof search.

@@

The \emph{superposition calculus} is of particular interest
because it is used in the most successful contemporary \gls{fol} \glspl{atp}.
A \emph{\gls{sot}} \cite{DBLP:journals/logcom/BachmairG94} constrains the inferences of the superposition calculus.
